---
title: "Example Report"
author: "Tychobra"
date: "`r Sys.time()`"
output: html_document
params:
  exposure: NA
  frequency: NA
  retention_per_claim: NA
  retention_aggregate: NA
  trend: NA
  trend_year: NA
  development: NA
  shock_cutoff: NA
  shock_prob: NA
  plot_func: NA
  plot_args: NA
  claims: NA
---

<style type="text/css">
.table {
  width: 200px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(scipen=999)
library(dplyr)
```

<br />

### Non Claim Inputs

- **exposure:** `r format(params$exposure, big.mark = ",")`
- **frequency:** `r params$frequency`
- **retention per claim:** `r format(params$retention_per_claim, big.mark = ",")`
- **retention aggregate:** `r format(params$retention_aggregate, big.mark = ",")`
- **annual trend:** `r format(params$trend, big.mark = ",")`
- **trend year:** `r params$trend_year`
- **shock cutoff:** `r format(params$shock_cutoff, big.mark = ",")`
- **shock probability:** `r paste0(params$shock_prob * 100, "%")`
- **development factors:**

```{r}
out <- params$development
names(out) <- c("Accident Year", "CDF")
knitr::kable(out)
```

<br />

### Plots

```{r, warning=FALSE, results="asis"}
library(highcharter)
plot_args <- params$plot_args
out <- vector("list", length = length(plot_args))
for (i in seq_along(plot_args)) {
  out[[i]] <- do.call(params$plot_func, plot_args[[i]])
  
}
htmltools::tagList(out)  
```

<br />

### Claims used to create sample for bootstrap

```{r}
out <- params$claims
out <- out %>%
  mutate(value = format(round(value, 2), big.mark = ","))

knitr::kable(out, align = c("c", "c", "r"))
```
