---
geometry: "left=1cm,right=1cm,top=2cm,bottom=2cm"
params:
  data: !r NA
  val_date: !r as.Date("2019-01-31")
output: 
  pdf_document: 
    keep_tex: yes
    latex_engine: xelatex
    includes:
      in_header: mystyles.sty
classoption: landscape
---

```{r options, message = FALSE, warning = FALSE, echo = FALSE}
# determine if running in Shiny or not
is_in_shiny <- if(is.null(shiny::getDefaultReactiveDomain())) FALSE else TRUE
if (is_in_shiny == TRUE) shiny::incProgress(amount = 0, message = "Setting Up")

# packages
library(dplyr)
library(lubridate)
library(knitr)
library(kableExtra)
library(summaryrow) # remotes::install_github("merlinoa/summaryrow")

# knitr options
knitr::opts_chunk$set(
  echo = FALSE
)

options(knitr.table.format = "latex")

```

```{r}
val_date_display <- as.character(format(params$val_date, format = "%B %d, %Y"))
prior_date_display <- as.character(format(params$val_date - years(1), format = "%B %d, %Y"))
date_now <- as.character(format(Sys.Date(), format = "%B %d, %Y"))
```

\begin{titlepage}
  
  \setlength{\headsep}{0.4in}
  
  \includegraphics[width=8cm]{./images/tychobra_logo_blue_co_name}\\
  
  \vspace{2.5cm}
  
  \Huge
   
    \textbf{Example Client Name}\\
    \textbf{Workers' Compensation Claims Report}
  \Huge
  
  \huge
    `r paste0("Data Evaluated as of ", val_date_display)`\\
    `r paste0("Report Generated on ", date_now)`
  \huge
  \vspace{1mm}
  
  \Large
   \noindent Created By Tychobra
  \Large
  \\
  
  
  \vspace{5cm}
  
  \flushright{\includegraphics[width=1.5cm]{./images/tychobra-logo-blue}}
 
\end{titlepage}


\fancyhead[R]{Claims Report \\ As of `r val_date_display`}

\fancyfoot[L]{\includegraphics[width=0.75cm]{./images/tychobra-logo-blue}}
\fancyfoot[C]{\small Page \thepage\\}
\fancyfoot[R]{`r as.character(format(Sys.time(), format = "%b %d, %Y %H:%M:%S"))`}

\captionsetup[table]{labelformat=empty}

\renewcommand{\arraystretch}{2}



```{r data_prep, eval = TRUE}
if (is_in_shiny) shiny::incProgress(amount = 0.25, message = "Loading Data")

# parameters
data_ <- if (length(params$data) == 1) readRDS("../../data/trans.RDS") else params$data
eval_ <- params$val_date


#' loss_run
#' 
#' view losses as of a specific date
#' 
#' @param val_date
#' 
loss_run <- function(val_date) {
  data_ %>%
    filter(transaction_date <= val_date) %>%
    group_by(claim_num) %>%
    top_n(1, wt = trans_num) %>%
    ungroup() %>%
    mutate(reported = paid + case) %>%
    arrange(desc(transaction_date))
}

# data prep
lr_current <- loss_run(eval_)
lr_prior <- loss_run(eval_ - years(1))
```


\newpage
### Exhibit 1
### Summary of Loss & ALAE
### Evaluated as of `r val_date_display`

\vspace{1cm}

```{r table_1, results = 'asis'}
if (is_in_shiny == TRUE) incProgress(amount = 0.25, message = "Generating Table 1")

by_ay <- lr_current %>%
  mutate(
    year = as.character(lubridate::year(accident_date)),
    n_open = ifelse(status == "Open", 1, 0)
  ) %>%
  group_by(year) %>%
  summarize(
    paid = sum(paid),
    case = sum(case),
    reported = sum(reported),
    n_open = sum(n_open),
    n = n()
  ) %>%
  ungroup() %>%
  totals_row(
    cols = 2:6,
    label_col = 1
  )


knitr::kable(
  by_ay,
  booktabs = TRUE,
  linesep = "",
  align = c(
    "c", 
    "r",
    "r",
    "r",
    "r",
    "r"
  ),
  col.names = c(
    "Accident Year",
    "Paid",
    "Case",
    "Reported",
    "Open",
    "Reported"
  ),
  escape = FALSE,
  digits = 0,
  format.args = list(big.mark = ",")
) %>%
  row_spec(0, align = "c") %>%
  kableExtra::row_spec(nrow(by_ay) - 1, hline_after = TRUE) %>%
  add_header_above(c(
    " " = 1, 
    "Loss & ALAE" = 3,
    "Number of Claims" = 2
  )) %>%
  #column_spec(1, border_right = TRUE) %>%
  kable_styling(full_width = TRUE, latex_options = c("striped"))
```


\newpage
### Exhibit 2
### Claims with change in paid >= 100,000
### Evaluated as of `r as.character(format(eval_, format = "%B %d, %Y"))`


\vspace{1cm}

```{r table_2, results = 'asis'}
if (is_in_shiny == TRUE) incProgress(amount = 0.25, message = "Generating Table 2")

out <- lr_current %>%
  select(claim_num, accident_date, claimant, state, status, paid, reported)

lr_prior_out <- lr_prior %>%
  select(claim_num, paid, reported)

out <- out %>%
  left_join(lr_prior_out, by = "claim_num") %>%
  mutate(
    paid_change = paid.x - paid.y,
    #case_change = case.x - case.y,
    reported_change = reported.x - reported.y
  ) %>%
  filter(paid_change >= 100000) %>%
  arrange(desc(paid_change))

headers <- c(5, 2, 2, 2)
names(headers) <- c(
  " ",
  paste0("As of ", val_date_display),
  paste0("As of ", prior_date_display),
  paste0("Change")
)

knitr::kable(
  out,
  booktabs = TRUE,
  linesep = "",
  escape = FALSE,
  #longtable = TRUE,
  align = c(
    "c",
    "c",
    "l",
    "c",
    "c",
    "r",
    "r",
    "r",
    "r",
    "r",
    "r"
  ),
  col.names = c(
    "Claim Number",
    "Accident Date",
    "Claimant",
    "State",
    "Status",
    "Paid",
    "Reported",
    "Paid",
    "Reported",
    "Paid",
    "Reported"
  ),
  digits = 0,
  format.args = list(big.mark = ",")
) %>%
  row_spec(0, align = "c") %>%
  column_spec(c(3), width = "4cm") %>%
  #column_spec(c(6, 8, 10), border_left = TRUE)  %>%
  kable_styling(full_width = FALSE, position = "center", latex_options = c("striped", "repeat_header")) %>%
  add_header_above(headers)
```
